%%
%% Beginning of file 'sample.tex'
%%
%% Modified 03 Nov 99
%%
%% This is a sample manuscript marked up using the
%% AASTeX v5.0 LaTeX 2e macros.

%% The first piece of markup in an AASTeX v5.0 document
%% is the \documentclass command. LaTeX will ignore
%% any data that comes before this command.

%% The command below calls the default manuscript style,
%% which will produce a double-spaced document on one column.
%% Examples of commands for other substyles follow. Use
%% whichever is most appropriate for your purposes.

\documentclass[preprint]{aastex}
\usepackage{amsmath}
\usepackage{html}

%% preprint produces a one-column, single-spaced document:

% \documentclass[preprint]{aastex}

%% preprint2 produces a double-column, single-spaced document:

% \documentclass[preprint2]{aastex}

%% If you want to create your own macros, you can do so
%% using \newcommand. Your macros should appear before
%% the \begin{document} command.
%%
%% If you are submitting to a journal that translates manuscripts
%% into SGML, you need to follow certain guidelines when preparing
%% your macros. See the AASTeX v5.0 Author Guide
%% for information.



%% If you wish, you may supply running head information, although
%% this information may be modified by the editorial offices.
%% The left head contains a list of authors,
%% usually a maximum of three (otherwise use et al.).  The right
%% head is a modified title of up to roughly 44 characters.  Running heads
%% will not print in the manuscript style.


%% This is the end of the preamble.  Indicate the beginning of the
%% paper itself with \begin{document}.

\begin{document}

%% LaTeX will automatically break titles if they run longer than
%% one line. However, you may use \\ to force a line break if
%% you desire.

\title{The SDSS Telescope Performance Monitor}

\author{Peregrine M. McGehee\\5 March 2004}

The document is maintained by Peregrine M. McGehee at Los Alamos
National Laboratory and the Department of Astronomy at New Mexico
State University. Questions and comments should be directed to
{\it peregrin\_at\_apo.nmsu.edu}.

A gzip-ed Postscript version of this document is available at
\htmladdnormallink{tpm.ps.gz}{../tpm.ps.gz}. 
The \LaTeX{} source, figures, and build scripts are in SDSS CVS
as part of the {\tt tpm} module. 

%% Use \author, \affil, and the \and command to format
%% author and affiliation information.
%% Note that \email has replaced the old \authoremail command
%% from AASTeX v4.0. You can use \email to mark an email address
%% anywhere in the paper, not just in the front matter.
%% As in the title, you can use \\ to force line breaks.

\section{Introduction}
The Telescope Performance Monitor displays and archives engineering data
using the infrastructure supplied by the Experimental Physics and 
Industrial Control System (EPICS) toolkit.
Detailed information concerning EPICS can be found at the project home
page at Argonne National Laboratory:
\htmladdnormallink{http://epics.aps.anl.gov/epics}{http://epics.aps.anl.gov/epics}

The real-time component of the TPM is implemented on two Motorola 
MV162 (Petra) VMEbus computers running the vxWorks operating system 
(v5.1.1) and version R3.13.5 of EPICS iocCore. These two MV162s, 
hereafter referred to as Input-Output Controllers (IOCs), acquire 
information about the Sloan telescope and ancillary systems using a variety of interfaces. 

This document begins with a discussion of the information needed
for developers followed by an overview of the operator displays.
The breakdown of the TPM into logical subsystems is presented. Next the
physical interfaces used by the TPM are described.

Within the section on alarms we categorize those native TPM alarms
that are transmitted to IOP and watcher. The document concludes
with a series of tables organized by logical subsystem that
describe all of the TPM process variables.

\include{developers}

\include{displays}

\include{subsystems}

\include{interfaces}

\include{alarms}

\section{Channel Reports By Subsystem}

To provide an overview of the individual TPM channels we present
a series of tables for each logical subsystem. The channels within
each subsystem are separated into those that are written into the
TPM logs by the EPICS channel archiver and those that are not.

For each channel we provide the full process variable name 
including the database record field. The default field name
is ``.VAL''. In addition to the process variable name we
give the scanning period within the EPICS database, the device
driver specification, and the channel description.

This section is automatically generated from the ASCII database
files found in {\tt<tpmbase>}/db and the ChannelArchiver
configuration files located in {\tt<tpmbase>}/ChanArch/config. The
documentation generation process uses a combination of bash scripts
and Tcl program driven by {\tt<tpmbase>}/doc/gentpmdoc.sh.

The calling sequence is:\\
\$ gentpmdoc.sh {\tt<tpm\_root>} \\
where {\tt<tpm\_root>} is the top of a TPM distribution directory, e.g.
/p/tpmbase or /usrdevel/peregrin/tpm.

\include{tpm_channelreport}

\end{document}
